Constraining speed of gravitational wave and Newton's constant in binary systems

### 2022-12-19 paper.tex
introduction

\documentclass{article}
\usepackage{amsmath}
\def\d{\mathrm{d}}
\def\p{\partial}
\begin{document}

@@

\section{Conclusion}

In this paper, for a binary GW source, we have provided a method to constrain constant $c$ and $G$ in the location of the source by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distance of the source. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item the speeds of two components of the binary are low;
    \item in a spherical region where the binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of the binary;
    \item both $c$ and $G$ are only related to $r$, the distance from the binary;
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ is depended on the uncertainties of the results of measuring the luminosity distance of the source, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$,  results of using GW observation data to constrain the luminosity distance of the source in unreached high precision are needed.

>>>>

\documentclass{article}
\usepackage{amsmath}
\def\d{\mathrm{d}}
\def\p{\partial}
\title{Constraining speed of gravitational wave and Newton's constant in binary systems}
\author{An Jiachen}
\begin{document}

\maketitle

\section{Introduction}

Any constant varying in space and/or time will induce a violation of the universality of free fall, and various experiments have been conducted on it. Methods of constraining temporal variation of Newton's constant $G$ in binary systems with the assumption that speed of gravitational wave $c$ is constant have been provided. In this paper we concentrate on spatial variations. We provided a method to constrain $c$ and $G$ in binary systems by comparing the results, which are obtained by using gravitational wave (GW) and electromagnetic wave (EMW) observation data and methods in former researches, of measuring the luminosity distances of the binary systems.

@@

\section{Conclusion}
In this paper, we provided a method to constrain speed of GW $c$ and Newton's constant $G$ in binary systems by comparing the results, which are obtained by using GW and EMW observation data and methods in former researches, of measuring the luminosity distances of the binary systems. This method can be practicable when \eqref{lorentz} and \eqref{maxwell} are vaild, together with:
\begin{enumerate}
    \item the speeds of two components of binary are low;
    \item in a spherical region where binary is located at the center, $c$ and $G$ are nearly constants, and the radius of the region is much greater than the distance between two components of binary;
    \item both $c$ and $G$ are only related to $r$, the distance from binary;
    \item $\frac{\d}{\d r}\ln c$, $\frac{\d}{\d r}\ln G$, $\frac{\d^2}{\d r^2}\ln c$, $\frac{\d^2}{\d r^2}\ln G$ are all small.
\end{enumerate}
The strength of constraining $c$ and $G$ by using method provided in this paper is depended on the uncertainties of the results of measuring the luminosity distances of the binary systems, especially that by using GW observation data. Therefore, to strongly constrain $c$ and $G$, results of using GW observation data to constrain the luminosity distances of the binary systems in unreached high precision are needed.
